---
title: "Lab results — first look"
output: html_document
---

Synthetic data. See `data/README.md`.

> **This document has the same deliberate flaw as `notebooks/01_explore.ipynb`.**
> Run the chunks one at a time from top to bottom and it looks fine — because you will
> have defined things along the way in your global environment. Then try
> **Knit**, and watch it fail.
>
> That is the R version of Restart & Run All, and you get it for free: knitting always
> starts a fresh R session, so it cannot see anything hiding in your environment.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# knitr sets the working directory to the project root for .Rmd files in a
# subfolder only if you tell it to. This is the reproducible way to say it.
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r load}
source("R/cleaning.R")

raw <- load_labs("data/labs.csv")
cat(nrow(raw), "rows loaded\n")
```

## Clean it

One `source()`, not five pasted chunks. That is the whole argument for `R/cleaning.R` —
change a cleaning rule and it changes everywhere at once.

```{r clean}
labs <- qc_flags(tidy_labs(raw))

cat(nrow(labs), "rows after cleaning (1 exact duplicate dropped)\n")
cat("sites:", paste(sort(unique(labs$site)), collapse = ", "), "\n")
```

## Flag the high-glucose visits

```{r flag}
# `threshold` is not defined anywhere in this document.
#
# If you have been working in this session for a while, it is probably sitting in
# your global environment from something you ran earlier — so this chunk will run
# happily for YOU and fail for everyone else, including future you on a clean start.
#
# Worse, in RStudio's default configuration that value can survive quitting the
# program entirely, because the workspace gets saved to .RData and restored at
# startup. Turn that off: Tools > Global Options > General.
flagged <- flag_high_glucose(labs, threshold)

cat(nrow(flagged), "visits at or above the threshold\n")
flagged[, c("subject_id", "glucose_mmol_l", "hba1c_percent", "site")]
```

## Mean values by site

```{r summary}
summarise_by_site(labs)
```

---

## Your turn

1. **Knit this document.** It fails at the `flag` chunk — the one that ran fine interactively.
2. Read the error: `object 'threshold' not found`.
3. Ask the uncomfortable question: *that output was real. Someone could have put it in a paper.*
4. Fix it — define `threshold <- 7.0` in the chunk where it belongs, so the intent is
   written down rather than remembered.
5. Knit again. Now it is reproducible.

Two more things worth trying, in this order:

- Run `rm(list = ls())` and knit again. It still works, which proves `rm(list = ls())`
  was never the safety check you thought it was — it clears variables but leaves
  packages and options loaded.
- **Session → Restart R** (`Cmd/Ctrl+Shift+F10`), then source the whole thing. That is
  the real clean start.
